### 2024-01-03 Appendix.Rmd
fix fig appendix

```{r echo = FALSE, message = FALSE, fig.width=11.3, fig.height=8.6, fig.align = 'center',fig.cap = "Estimated statistical power for recovering the data-generating model (y-axis) as a function of sample size (x-axis) depending on (A) loading strength for lower versus higher inter-factor correlation and (B) inter-factor correlation for lower versus higher factor loadings. * denotes results from the original analyses in the main manuscript"}

@@

plot_load_model3 <- results_load_model3 %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            linewidth = 1.3,
            key_glyph = "rect") +
  geom_hline(
    yintercept = 95,
    linetype = "dashed",
    color = "#F29090",
    linewidth = 1.3
  ) +
  xlab('Sample size\n') + ylab('Power (%)') + 
  ggtitle('Inter-factor correlation = 0.3* \n') +
  scale_color_discrete('Loading       \nstrength') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 100),
    breaks = seq(0, 100, by = 20)
  ) +
  theme_plots

plot_load_model3_highcov <- results_load_model3_highcov %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            linewidth = 1.3,
            key_glyph = "rect") +
  geom_hline(
    yintercept = 95,
    linetype = "dashed",
    color = "#F29090",
    linewidth = 1.3
  ) +
  xlab('Sample size\n') + ylab('Power (%)') + ggtitle('Inter-factor correlation = 0.7\n') +
  scale_color_discrete('Loading \nstrength') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 100),
    breaks = seq(0, 100, by = 20)
  ) +
  theme_plots

plot_cov_model3_lowload <- results_cov_model3_lowload %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(cov1))) +
  geom_point() +
  geom_line(alpha = 0.4,
            linewidth = 1.3,
            key_glyph = "rect") +
  geom_hline(
    yintercept = 95,
    linetype = "dashed",
    color = "#F29090",
    linewidth = 1.3
  ) +
  xlab('Sample size\n') + ylab('Power (%)') + 
  ggtitle('Factor loading = 0.5\n') +
  scale_color_discrete('Inter-factor \ncorrelation') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 100),
    breaks = seq(0, 100, by = 20)
  ) +
  theme_plots

plot_cov_model3 <- results_cov_model3 %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(cov1))) +
  geom_point() +
  geom_line(alpha = 0.4,
            linewidth = 1.3,
            key_glyph = "rect") +
  geom_hline(
    yintercept = 95,
    linetype = "dashed",
    color = "#F29090",
    linewidth = 1.3
  ) +
  xlab('Sample size\n') + ylab('Power (%)') + 
  ggtitle('Factor loading = 0.7*\n') +
  scale_color_discrete('Inter-factor \ncorrelation') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 100),
    breaks = seq(0, 100, by = 20)
  ) +
  theme_plots

joined_plot <-
  ggarrange(plot_cov_model3_lowload,
            plot_cov_model3,
            plot_load_model3,
            plot_load_model3_highcov,
            ncol = 2,
            nrow = 2)
joined_plot

>>>>

```{r echo = FALSE, message = FALSE, fig.width=11.3, fig.height=10.4, fig.align = 'center',fig.cap = "Estimated statistical power for recovering the data-generating model (y-axis) as a function of sample size (x-axis) depending on (A) loading strength for lower versus higher inter-factor correlation and (B) inter-factor correlation for lower versus higher factor loadings. * denotes results from the original analyses in the main manuscript"}

@@

plot_load_model3 <- results_load_model3 %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            linewidth = 1.3,
            key_glyph = "rect") +
  geom_hline(
    yintercept = 95,
    linetype = "dashed",
    color = "#F29090",
    linewidth = 1.3
  ) +
  xlab('Sample size\n') + ylab('Power (%)') + 
  ggtitle('A) \n\nInter-factor correlation = 0.3* \n') +
  scale_color_discrete('Loading\nstrength   ') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 100),
    breaks = seq(0, 100, by = 20)
  ) +
  theme_plots

plot_load_model3_highcov <- results_load_model3_highcov %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            linewidth = 1.3,
            key_glyph = "rect") +
  geom_hline(
    yintercept = 95,
    linetype = "dashed",
    color = "#F29090",
    linewidth = 1.3
  ) +
  xlab('Sample size\n') + ylab('Power (%)') + 
  ggtitle('\n\nInter-factor correlation = 0.7 \n') +
  scale_color_discrete('Loading \nstrength   ') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 100),
    breaks = seq(0, 100, by = 20)
  ) +
  theme_plots

plot_cov_model3_lowload <- results_cov_model3_lowload %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(cov1))) +
  geom_point() +
  geom_line(alpha = 0.4,
            linewidth = 1.3,
            key_glyph = "rect") +
  geom_hline(
    yintercept = 95,
    linetype = "dashed",
    color = "#F29090",
    linewidth = 1.3
  ) +
  xlab('Sample size\n') + ylab('Power (%)') + 
  ggtitle('B) \n\nFactor loading = 0.5\n') +
  scale_color_discrete('Inter-factor \ncorrelation') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 100),
    breaks = seq(0, 100, by = 20)
  ) +
  theme_plots

plot_cov_model3 <- results_cov_model3 %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(cov1))) +
  geom_point() +
  geom_line(alpha = 0.4,
            linewidth = 1.3,
            key_glyph = "rect") +
  geom_hline(
    yintercept = 95,
    linetype = "dashed",
    color = "#F29090",
    linewidth = 1.3
  ) +
  xlab('Sample size\n') + ylab('Power (%)') + 
  ggtitle('\n\nFactor loading = 0.7*\n') +
  scale_color_discrete('Inter-factor \ncorrelation') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 100),
    breaks = seq(0, 100, by = 20)
  ) +
  theme_plots

joined_plot <- plot_grid(
  plot_load_model3
  , plot_load_model3_highcov
  , plot_cov_model3_lowload
  , plot_cov_model3
  , align = "hv"
  , ncol = 2
)
joined_plot

### 2024-01-03 manuscript.Rmd
fix fig appendix

repro:
  packages:
    - lavaan
    - papaja
    - tidyverse
    - ggpubr
    - SimDesign
    - here
    - aaronpeikert/repro@5a920f7
    - gert
  tlmgr:
    - apa6
    - threeparttable
    - endfloat
    - framed
    - was
    - multirow
    - threeparttablex
    - environ
    - trimspaces
    - xpatch
    - csquotes
  scripts:
    - R/funs.R
---

```{r setup, include = FALSE}
library(papaja)
library(tidyverse)
library(ggpubr)
library(here)
library(SimDesign)

>>>>

repro:
  packages:
    - lavaan
    - papaja
    - tidyverse
    - ggpubr
    - SimDesign
    - here
    - aaronpeikert/repro@5a920f7
    - gert
    - cowplot
  tlmgr:
    - apa6
    - threeparttable
    - endfloat
    - framed
    - was
    - multirow
    - threeparttablex
    - environ
    - trimspaces
    - xpatch
    - csquotes
  scripts:
    - R/funs.R
---

```{r setup, include = FALSE}
library(papaja)
library(tidyverse)
library(ggpubr)
library(here)
library(SimDesign)
library(cowplot)
